---
title: "E.Paul_OneNumStory"
author: "Evelyn Paul"
date: "2023-11-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(knitr)
library(stringr)

elf <- read.csv("https://raw.githubusercontent.com/mac-comp112-f23/project-bear/main/elfman_final.csv")
pem <- read.csv("https://raw.githubusercontent.com/mac-comp112-f23/project-bear/main/pemb_final.csv")
zim <- read.csv("https://raw.githubusercontent.com/mac-comp112-f23/project-bear/main/zimmer_final.csv")

```
```{r}

zimmer_sorted <- zim %>% arrange(desc(averageRating))
pemb_sorted <- pem %>% arrange(desc(averageRating))
elfman_sorted <- elf %>% arrange(desc(averageRating))

head(zimmer_sorted, 5)
head(pemb_sorted, 5)
head(elfman_sorted, 5)
```
```{r}

top_elfman <- elf %>% 
  arrange(desc(averageRating)) %>% 
  slice(1) %>% 
  mutate(composer = "Danny Elfman")

top_pemb <- pem %>% 
  arrange(desc(averageRating)) %>% 
  slice(1) %>% 
  mutate(composer = "Daniel Pemberton")

top_zimmer <- zim %>% 
  arrange(desc(averageRating)) %>% 
  slice(2) %>% 
  mutate(composer = "Hans Zimmer")

# Combine the top scores into one data frame
top_scores <- bind_rows(top_elfman, top_pemb, top_zimmer)

# Select the relevant columns
top_scores <- top_scores %>% select(Composer = composer, Title = primaryTitle, Score = averageRating, Year = startYear)

# Use kable to create a nice table
kable_table <- kable(top_scores, format = "markdown", caption = "Highest Rated Scores by Composer")

# Print the table
kable_table
```

> Symphonies of Success 


In the realm of cinematic scores, Danny Elfman, Daniel Pemberton, and Hans Zimmer stand out. A single number for each – their highest rated work  – tells a larger story of their artistry

Not many know that Danny Elfman composed for Chicago (2002). Those who do, however, give it a perfect score. The score complements the film’s energy and attitude, and it has remained in the top ten most popular movies at the box office for two decades. In 2016, Hans Zimmer’s work on Planet Earth II helped propel it to critical acclaim. His music alongside stunning visuals of the natural world captivated viewers of every age. In the case of Daniel Pemberton, an 8.9 rating for his work on “Spider-Man: Across the Spider-Verse'' is a significant achievement for a score released in 2023. Pemberton’s is innovative, fresh, and contemporary, and has the perfect sound for bringing a classic superhero into a new era. 

These numbers—10.0, 8.9, and 9.5—aren’t just abstract values. Each rating tells a story about the composer behind the score. All three composers are unique in their style and substance, as well as what they work on, but they share a common trait. These numbers tell us that Elfman, Pemberton, and Zimmer all have an unparalleled talent for musical storytelling. They have touched millions worldwide, significantly raising the bar for contemporary composers. 


